Quantum Algorithms for Portflolio Optimisation and Option pricing

### 2024-06-05 project/paper-v2.tex
update project paper QAOA

In a similar fashion, the Quantum Approximate Optimisation Algorithm (QAOA) is another VQA that was first 
conceived as

>>>>

In a similar fashion, the Quantum Approximate Optimisation Algorithm (QAOA) is another VQA that was first 
conceived by Farhi et al. \cite{Farhi2014} for combinatorial optimisation problems (e.g. Max-Cut).

Mathematically, we can see the combinatorial optimisation problem as a graph with $m$ edges and $n$ vertices. Then, define a bitstring $x = $

\begin{figure}[h!]
\centering 
\includegraphics[width=0.35\textwidth]{combinatorial-problem.pdf}
  \caption{\label{fig:combinatorial} A graph representation of a combinatorial optimisation problem. Adapted from \cite{Baker2022}.} 
\end{figure}
